### 2012-05-17 GUIErrorDetector/paper/abstract.tex
fix typoes, inconsistency
remove VirgoFTP

We implemented our technique and instantiated it for four popular Java GUI
platforms: SWT, the Eclipse plugin development framework, Swing, and
Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
found 5 previously-known errors and 7 new ones.

@@

>>>>

We implemented our technique and instantiated it for four popular Java GUI
frameworks: SWT, the Eclipse plugin framework, Swing, and
Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
found \oldbugs previously-known errors and \newbugs new ones.

@@

\smallskip
\noindent
\textbf{Categories and Subject Descriptors}:  
D.2.5 [Software Engineering]: Testing and Debugging.
\\
\textbf{General Terms: }
Reliability, Experimentation.
\\
\textbf{Keywords: }
Static analysis, invalid thread access error.

\label{this-label-makes-etags-order-this-file-properly}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "guierror"
%%% TeX-command-default: "PDF"
%%% End:

%  LocalWords:  multithreaded SWT plugin LOC
